pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools

### 2020-02-27 draft.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{{main_figures/clustering_files/figure-html/clustering-1.png}}
    \caption{\textbf{Evaluation of clustering methods.} Clustering accuracy of common clustering tools in combination with \textit{sctransform} and standard Seurat's normalization.}
    \label{fig:figure9}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.75,keepaspectratio]{main_figures/pipeComp_summary.png}
    \caption{\textbf{Recommendations of tools from filtering, to clustering.}}
    \label{fig:figure11}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{{main_figures/clustering_files/figure-html/clustering-1.png}}
    \caption{\textbf{Evaluation of clustering methods.} Clustering accuracy of common clustering tools in combination with \textit{sctransform} and standard Seurat's normalization.}
    \label{fig:figure9}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.08,keepaspectratio]{main_figures/pipeComp_summary.png}
    \caption{\textbf{Recommendations of tools from filtering to clustering.}}
    \label{fig:figure11}
\end{figure}
